Age-related changes in plant growth and traits

### 2016-11-10 scripts/RA_figs_20160627.Rmd
continued trying to fix problems with accounting

```{r}
data <- dplyr::select(SummarySppAge[["mean"]],species,age,repro_inv,growth_leaf,leaf_replacement,growth_stem,leaf_shed)

@@

#data <- subset(data,species=="BOLE")
data <- split(data, data$species)

@@

  if(spp=="BAER"|spp=="EPMI"|spp=="GRBU"|spp=="HATE"|spp=="PELA"|spp=="PUTU"|spp=="LEES"|spp=="PEPU") {
  polygon(x=c(1.4,32,32,1.4),y=c(1,1,0,0),col="burlywood4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
                                           data[[spp]]$prop_leaf_replacement[5],data[[spp]]$prop_leaf_replacement[6],0,0),col="darkseagreen4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
                                         data[[spp]]$prop_leaf_expand[5],data[[spp]]$prop_leaf_expand[6],0,0),col="darkseagreen2",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
                                          data[[spp]]$prop_repro[5],data[[spp]]$prop_repro[6],0,0),col="coral3",density=NA)
  text(20,data[[spp]]$prop_repro[6]*.4,"reproductive")
  text(1.5,data[[spp]]$prop_leaf_expand[1]*.3,"additional leaves",adj=0)
  text(5,data[[spp]]$prop_leaf_replacement[4]*.6,"replacement leaves",adj=0)
  text(15,0.9,"additional stems",adj=0)
  }
  extra.top.left.logx(labels.spp.full(spp),3,1)
}
```

>>>>

```{r}
pdf("figs2/RA/Figure_1_stacked_lines.pdf", height=11.5, width=8)
plot
par(mfrow=c(4,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2))

data <- dplyr::select(SummarySppAge[["mean"]],species,age,repro_inv,growth_leaf,leaf_replacement,growth_stem,leaf_shed)

@@

data <- split(data, data$species)

@@

  if(spp=="BAER"|spp=="EPMI"|spp=="GRBU"|spp=="HATE"|spp=="PELA"|spp=="PUTU"|spp=="LEES"|spp=="PEPU") {
  polygon(x=c(1.4,32,32,1.4),y=c(1,1,0,0),col="burlywood4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
                                           data[[spp]]$prop_leaf_replacement[5],data[[spp]]$prop_leaf_replacement[6],0,0),col="darkseagreen4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
                                         data[[spp]]$prop_leaf_expand[5],data[[spp]]$prop_leaf_expand[6],0,0),col="darkseagreen2",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
                                          data[[spp]]$prop_repro[5],data[[spp]]$prop_repro[6],0,0),col="coral3",density=NA)
  text(20,data[[spp]]$prop_repro[6]*.4,"reproductive")
  text(1.5,data[[spp]]$prop_leaf_expand[1]*.3,"additional leaves",adj=0)
  text(5,data[[spp]]$prop_leaf_replacement[4]*.6,"replacement leaves",adj=0)
  text(15,0.9,"additional stems",adj=0)
  }
  extra.top.left.logx(labels.spp.full(spp),3,1)
}
